### 2018-04-29 paper/design.tex
squad overlay being done

This section presents the \name protocol in detail.
Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file $f$ through \name; they start by sharing some information out-of-band, e.g. from their smartphones.
More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Probabilistic Onion Routes (POR).
PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that will relay their messages.
From there on, Alice and Bob add the POR information to the headers of their subsequent file exchange messages, such that the file transfer remains secret to anyone but them.

@@

The privacy objectives of our system require encryption primitives that we first detail in section~\ref{BuildingBlocks}. The other constituents of \name are depicted in figure~\ref{fig:outline}.
On top, the devices of each user are circled in gray, and form a user's device squad. The squad online members communicate among themselves: they exchange files and messages information, and cooperate to predict the user's future behavior. This first protocol is called the \emph{squad overlay} and will be discussed in section~\ref{sec:squad_overlay}.
%On top we see that each user's devices (shown as clouds) communicate with one another through a dissemination protocol---coined the \emph{squad overlay}---that will be discussed in section~\ref{sec:squad_overlay}. 
Below, we see all devices connected in a random graph: each online device gives information about itself. This \emph{global overlay} will be covered in section~\ref{sec:global_overlay}.
The information brought by these overlays allows devices to securely and reliably exchange messages between users, as will be explained in section~\ref{sec:message_passing}.
Given this message passing protocol, users can privately exchange files, as shown in the bottom of the figure. We will cover this ultimate goal in section~\ref{sec:file_exchange}.

>>>>

This section presents the \name protocol in detail.
Our goal is to enable private and reliable file exchange between users participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file $f$ through \name; they start by sharing some information out-of-band, e.g. from their smartphones.
More precisely, they exchange metadata on $f$, encryption keys, and agree upon a Probabilistic Onion Routes (POR).
PORs are our adaptation of onion routes, allowing secret communication between two entities despite the unreliability of the nodes that relay their messages.
From there on, Alice and Bob add the POR information to the headers of their subsequent file exchange messages, such that the file transfer remains secret to anyone but them.

@@

The privacy objectives of our system require encryption primitives that we first detail in section~\ref{BuildingBlocks}. The other constituents of \name are depicted in figure~\ref{fig:outline}.
On top, the devices of each user are circled in gray, and form a user's device squad. The squad online members communicate among themselves: they exchange files and messages information, and cooperate to predict the user's future behavior. This first protocol is called the \emph{Squad Overlay} and will be discussed in section~\ref{sec:squad_overlay}.
%On top we see that each user's devices (shown as clouds) communicate with one another through a dissemination protocol---coined the \emph{squad overlay}---that will be discussed in section~\ref{sec:squad_overlay}. 
Below, we see all devices connected in a random graph: each device gives information about itself to random nodes when it is online. 
This \emph{Global Overlay} will be covered in section~\ref{sec:global_overlay}.
The information brought by these overlays allows devices to securely and reliably exchange messages between users, as will be explained in section~\ref{sec:message_passing}.
Given this message passing protocol, users can privately exchange files, as shown in the bottom of the figure. We will cover this ultimate goal in section~\ref{sec:file_exchange}.

### 2018-04-29 paper/squad-overlay-design.tex
yaaaay, outline figure
squad overlay being done

\section{User model} 
\label{sec:user_model}

We consider many users owning several devices, that they freely turn on and off depending on their location and will.
The participants' devices are the only nodes constituting our system; the unreliability of their connectivity has to be taken for granted.

We will first present a model of each user's behavior, that will drive the connection intervals of our system's nodes.
%Then, we will show how devices can predict the future user's behavior given the model.

\subsection{A model of the user's behavior}
\label{sub:a_model_of_the_user_s_behavior}

>>>>

\subsection{The Squad Overlay} 
\label{sec:squad_overlay}

At the root of \name is predictive routing.
%By sharing information among themselves, a user's devices (her \emph{squad}) can model her behavior.
Our goal here is that each online device predicts the probability that it stays online in the near future.
This probability will later be used to create Probabilistic Onion Routes (POR).
A device's connection depends on the activity of its user; thus, a user's devices (her \emph{squad}) want to predict her future behavior.

In this section, we only take interest in one user (called Alice) and her squad.

% Each of Alice's (and Bob's) devices will keep track of its own online and 
% offline behavior.
% They will use a protocol like Sprinkler~\cite{luxey:hal-01704172} to learn about 
% each other's online--offline behavior.
% \commentDaniel{Is that correct?}
% This allows Alice's device swarm to infer a behavioral model for the device 
% swarm and do internal scheduling based on the probability of being online.

\subsubsection{Sharing the user's behavior} % (fold)
\label{sub:sharing_knowledge}

Online devices want to know whether they are likely to stay online in the near future.
Taken separately, each device only knows local information: when Alice used it, and maybe mobility information if it is mobile.
When combining these informations, though, we obtain a sequence of the user's behavior that is far more complete.
For instance, the probability that Alice uses her home computer and workstation simultaneously is null: these devices are too far apart.

The Squad Overlay leverages on a probabilistic dissemination protocol, \textsc{Sprinkler}~\cite{luxey:hal-01704172}, that does just that: 
it allows one's devices to inform one another every time the user performs an action (under the condition that no actions are concurrent).
Previous work in our team~\cite{luxey:cascade} showed that \textsc{Sprinkler} is resilient to devices churn: 
devices let each other know of what they have missed while offline.
We thus employ \textsc{Sprinkler} to disseminate the user's activity to its squad.

% Each device initially only knows when it is connected, which is not sufficient to make reliable predictions on whether it is likely to stay online.
% If they knew the other devices' connection and disconnection times, they 
% To make a model of the user's behavior, they need to know the whole observation sequence $O$: which device is online at each time step.
% To do so, they employ a probabilistic dissemination protocol, 
% \textsc{Sprinkler}~\cite{luxey:hal-01704172}.
% This allows devices to gossip any new connection information to random peers in 
% the local swarm, ensuring that all devices know the full observation sequence 
% with a very high probability.
% \textsc{Sprinkler} has shown resilient to device churn~\cite{luxey:cascade}, and 
% is thus perfectly suited for our purpose, where a user's devices often 
% disconnect and reconnect.

% subsection sharing_knowledge (end)

\subsubsection{Other uses of the Squad Overlay} % (fold)
\label{ssub:other_uses_of_the_squad_overlay}

In addition to user's behavior, devices firstly share user-chosen files location: when Alice wants to share a file $f$ that resides on her home computer, using her smartphone as the exchange initiator, her smartphone knows where $f$ is located and can create the route accordingly. 
Secondly, each device is also informed of its user's ongoing file transfers.

\name knows two message types (as will be covered in~\ref{sec:file_exchange}): file chunk, and acknowledgment.
Alice typically wants to receive a file on one particular device; respectively, only one of her devices is interested in acknowledging reception of the file chunks it is sending.
However, \name allows all squad members to receive messages destined to Alice.
Thus, the third complementary purpose of the Squad Overlay is to relay messages among the squad: when a message is not destined to the device that received it, the receiver forwards the message to its final destination.
% We consider many users owning several devices, that they freely turn on and off depending on their location and will.
% The participants' devices are the only nodes constituting our system; the unreliability of their connectivity has to be taken for granted.

% We will first present a model of each user's behavior, that will drive the connection intervals of our system's nodes.
% %Then, we will show how devices can predict the future user's behavior given the model.

\subsubsection{A model of the user's behavior}
\label{sub:a_model_of_the_user_s_behavior}
